Erosion leads to anisotropy in a porous medium

### 2018-12-28 docs/PhysicsPaper/StokesErosion.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
%\title{An eroding porous medium}
\title{The development of anisotropy in an eroding porous medium}
%
\author{M.~N.~J.~Moore}
\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Bryan D.~Quaife}
\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\begin{abstract}
We numerically simulate the erosion of a porous medium due to an internally flowing fluid. The solid constituents of the porous medium erode under the action of surface shear stress. As the particles shrink, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
\end{abstract}
\maketitle
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow. This method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can practically simulate the erosion of order hundreds of solid bodies.

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
\title{Erosion leads to anisotropy in a porous medium}
%\title{The development of anisotropy in an eroding porous medium}
%
\author{M.~N.~J.~Moore}
\affiliation{Department of Mathematics and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\author{Bryan D.~Quaife}
\affiliation{Department of Scientific Computing and Geophysical Fluid Dynamics Institute, Florida State University, Tallahassee, FL, 32306.}
\begin{abstract}
We numerically simulate the erosion of a porous medium due to an internally flowing fluid. The solid constituents of the porous medium erode under the action of surface shear stress. As the particles shrink, they elongate in the direction of the flow, giving rise to anisotropic conductivity of the porous medium.
\end{abstract}
\maketitle
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow. This method is documented, validated, benchmarked in \cite{Quaife2018}, and can practically simulate the erosion of order hundreds of solid bodies.
